Methods and Results

### 2022-10-05 ms.Rmd
Final update for the day

We also tested whether the variability in female fitness between the control and treatment group differed using the log Coefficient of Variation Ratio (lnCVR) that compared the coefficient of variation between control and treatment groups [@nakagawa2015meta]. Given lnCVR makes certain assumptions about mean-variance relationships, which are not always upheld [see @nakagawa2015meta], we also ran an 'arm-based' analysis using the log of the standard deviation (lnSD) in a multilevel meta-analytic model. See Supplemental Materials for full details. Both results provided similar conclusions about the change in variability between control and treatment groups so we only present lnCVR. Given lnCVR is a log ratio, we can only use ratio scale data to compute the effect size [@nakagawa2015meta]. In addition, data is assumed to be normally distributed; we tested this assumption using a modified Geary's test proposed by @laj2011. Only 6 effect sizes failed the test, and three of these were not ratio scale data. As such, we excluded these size effect size data from our lnCVR (and lnSD) analysis. In all cases, the CV of the control group was subtracted from the CV of the treatment group such that positive effect sizes suggest greater variance in the control group and negative effect sizes greater variability in the treatment group (after controlling for the mean).

@@

Experimentally manipulating female harm resulted in a strong decrease in female fitness overall (i.e., positive effect size with control group females having higher fitness than treatment groups: `r model1.1$beta`, 95% CI: `r model1.1$ci.lb` to `r model1.1$ci.ub`, $n_{effects}$ = `r model1.1$k.all`, $n_{study}$ = `r model1.1$s.nlevels[1]`). This effect held even when accounting for within-study non-independence (meta-analytic mean using Robust Variance Estimator: `r robust$beta`, 95% CI: `r robust$ci.lb` to `r robust$ci.ub`). Visual inspection of funnel plot asymmetry suggested evidence for publication bias (i.e., missed effects sizes with low precision when female harm was worse in control treatments) (Figure \@ref(fig:funnel)), which was confirmed through the identification of a significant slope between effect size and effective sample size ($\beta$ = `r model1.1_pub$beta[2]`, 95% CI: `r model1.1_pub$ci.lb[2]` to `r model1.1_pub$ci.ub[2]`). This result held true when accounting for heterogeneity using meta-regression models ($\beta$ =`r model1.1_pub_full$beta[2]`, 95% CI: `r model1.1_pub_full$ci.lb[2]` to `r model1.1_pub_full$ci.ub[2]`). Correcting for the possibility of missing studies resulted in the overall meta-analytic mean effect size being indistinguishable from zero (Corrected meta-analytic mean: `r model1.1_pub$beta[1]`, 95% CI: `r model1.1_pub$ci.lb[1]` to `r model1.1_pub$ci.ub[1]`). These findings suggest that additional empirical studies may change the overall magnitude of effects, possibly showing weaker effects then what is currently published, but our current state of knowledge suggests that female fitness is indeed compromised overall by male harm.

>>>>

We also tested whether the variability in female fitness between the control and treatment group differed using the log Coefficient of Variation Ratio (lnCVR) that compared the coefficient of variation between control and treatment groups [@nakagawa2015meta]. Given lnCVR makes certain assumptions about mean-variance relationships, which are not always upheld [see @nakagawa2015meta], we also ran an 'arm-based' analysis using the log of the standard deviation (lnSD) in a multilevel meta-analytic model. See Supplemental Materials for full details. Both results provided similar conclusions about the change in variability between control and treatment groups so we only present lnCVR. Given lnCVR is a log ratio, we can only use ratio scale data to compute the effect size [@nakagawa2015meta]. In addition, data is assumed to be normally distributed; we tested this assumption using a modified Geary's test proposed by @laj2011. Only 6 effect sizes failed the test, and three of these were not ratio scale data. As such, we excluded these effect size data from our lnCVR (and lnSD) analysis. In all cases, the CV of the control group was subtracted from the CV of the treatment group such that positive effect sizes suggest greater variance in the control group and negative effect sizes greater variability in the treatment group (after controlling for the mean).

@@

Experimentally manipulating female harm resulted in a strong decrease in female fitness overall (i.e., positive effect size with control group females having higher fitness than treatment groups: `r model1.1$beta`, 95% CI: `r model1.1$ci.lb` to `r model1.1$ci.ub`, $n_{effects}$ = `r model1.1$k.all`, $n_{study}$ = `r model1.1$s.nlevels[1]`) (Figure \@ref(fig:funnel)B). This effect held even when accounting for within-study non-independence (meta-analytic mean using Robust Variance Estimator: `r robust$beta`, 95% CI: `r robust$ci.lb` to `r robust$ci.ub`). Increased female harm also resulted in significantly higher variance in female fitness (Figure \@ref(fig:funnel)C) with females in treatment groups having an approximately `r (1-predict(model1_lnCVR, transf=exp)$pred)*100`% higher variance in fitness when controlling for the mean (`r model1_lnCVR$beta`, 95% CI: `r model1_lnCVR$ci.lb` to `r model1_lnCVR$ci.ub`, $n_{effects}$ = `r model1_lnCVR$k.all`, $n_{study}$ = `r model1_lnCVR$s.nlevels[1]`).

Visual inspection of funnel plot asymmetry suggested evidence for publication bias (i.e., missed effects sizes with low precision when female harm was worse in control treatments) (Figure \@ref(fig:funnel)), which was confirmed through the identification of a significant slope between effect size and effective sample size ($\beta$ = `r model1.1_pub$beta[2]`, 95% CI: `r model1.1_pub$ci.lb[2]` to `r model1.1_pub$ci.ub[2]`). This result held true when accounting for heterogeneity using meta-regression models ($\beta$ =`r model1.1_pub_full$beta[2]`, 95% CI: `r model1.1_pub_full$ci.lb[2]` to `r model1.1_pub_full$ci.ub[2]`). Correcting for the possibility of missing studies resulted in the overall meta-analytic mean effect size being indistinguishable from zero (Corrected meta-analytic mean: `r model1.1_pub$beta[1]`, 95% CI: `r model1.1_pub$ci.lb[1]` to `r model1.1_pub$ci.ub[1]`). These findings suggest that additional empirical studies may change the overall magnitude of effects, possibly showing weaker effects then what is currently published, but our current state of knowledge suggests that female fitness is indeed compromised overall by male harm.
